Awareness of Stack Overflow Users to\\ Outdated and License-violating Code:\\ The Online Survey

### 2017-08-28 cloverflow_technical_report/cloverflow_survey_rn.tex
Latest update of the technical report.

In this paper, we use the term ``answerers'' to refer to Stack Overflow users
who have high reputation, specifically the users with reputation from 963,731
(highest)  to 6,999. The answerers gain their reputation from answering
questions and receiving votes from other users. The reputation reflects trust
they gain from other users and their activeness in answering questions. We ask
the answerers the origins of source code snippets in their answers  and assess
their awareness of outdated and licensed code. We use the term ``visitors'' the
refer to developers, who may or may not have a Stack Overflow account but visit
Stack Overflow when facing programming problems. They copy example code snippets
that are relevant to their problems and reused them in their software. 
We ask Stack Overflow visitors, who copied code snippets from
Stack Overflow, about their experience of outdated or license-violating code.

@@

>>>>

In this paper, we use the term ``answerers'' to refer to Stack Overflow users
who have high reputation, specifically the users with reputation from 963,731
(highest)  to 6,999. The answerers gain their reputation from answering
questions and receiving votes from other users. The reputation reflects trust
they gain from other users and their activeness in answering questions. We ask
the answerers the origins of source code snippets in their answers  and assess
their awareness of outdated and licensed code. 
%We use the term ``visitors'' the
%refer to developers, who may or may not have a Stack Overflow account but visit
%Stack Overflow when facing programming problems. They copy example code snippets
%that are relevant to their problems and reused them in their software. 
%We ask Stack Overflow visitors, who copied code snippets from
%Stack Overflow, about their experience of outdated or license-violating code.

@@

We present our online survey results of Stack Overflow answerers in terms of their awareness to outdated code snippets and their software license.
